% Thresholds and justification for each architectural smell
%
% Baseline definition: a file touched in 1--2 commits, with 1--2 inbound or outbound
% dependencies, and fewer than 100 lines of code is considered the baseline (Low-boundary).
% Medium corresponds to roughly 3--5$\times$ the baseline metric;
% High corresponds to more than 7$\times$ the baseline metric.

\subsection*{Cyclic Dependency -- 0 occurrences}

No import cycles were detected in either layer. The backend follows a strict
directed acyclic graph: \texttt{server.js} $\to$ routes/ws $\to$ db. The
frontend follows React's convention of contexts depending on hooks, pages
depending on contexts, and components depending on pages. No file imports its
own ancestor.

\subsection*{Hub-Like Dependency -- 3 occurrences}

A file qualifies as a hub when its fan-out (number of modules it imports) or
fan-in (number of modules that import it) is significantly above the project
mean (which is $\approx$1.3 connections per file).

\begin{itemize}
  \item \textbf{High -- \texttt{backend/src/server.js}}: fan-out of 9 direct
    internal/external imports (oidc, metrics, genericApi, chat, utils, express,
    ws, cors, systeminformation). This is 7$\times$ the mean and makes
    \texttt{server.js} the single wiring point for the entire backend.

  \item \textbf{Medium -- \texttt{frontend/src/context/AuthContext.jsx}}:
    fan-in of 4--5 consumers (LoginPage, RegisterPage, TodoContext, ChatPage,
    App). Approximately 3--4$\times$ the mean; any interface change ripples
    to almost every page.

  \item \textbf{Low -- \texttt{backend/src/db/jsonDb.js}}: fan-in of 2
    (genericApi.js and chat.js). Slightly above the baseline but still
    contained.
\end{itemize}

\subsection*{God Component -- 3 occurrences}

A God Component is a module that accumulates multiple, unrelated
responsibilities. The threshold used here is $\geq$150 LOC \emph{and} $\geq$3
distinct responsibilities.

\begin{itemize}
  \item \textbf{High -- \texttt{backend/src/server.js} (396 LOC)}: at least 9
    responsibilities: HTTP/Express setup, route mounting, WebSocket server
    creation, connection upgrade, CPU metrics, memory metrics, disk metrics,
    network metrics, GPU metrics (with platform-specific branches for Windows
    PDH and Linux nvidia-smi), subscription management, and broadcast loop.
    At 4$\times$ the 100-LOC baseline and with more responsibilities than any
    other file, this is the most severe God Component.

  \item \textbf{High -- \texttt{frontend/src/pages/MetricsPage.jsx} (353 LOC)}:
    embeds 7 display sub-components (CpuCard, MemoryCard, UptimeCard,
    DiskCard, NetworkCard, GpuCard, plus bar/badge helpers) and 3 formatting
    utilities (\texttt{formatUptime}, \texttt{formatBytes},
    \texttt{formatSpeed}) in a single file. All metric feature work requires
    editing this file.

  \item \textbf{Medium -- \texttt{backend/src/routes/oidc.js} (194 LOC)}: 5
    HTTP endpoints (discovery, JWKS, authorize, login, token, userinfo), RSA
    key-pair generation, HTML form rendering, and all SQLite queries for user
    and token management. About 2$\times$ the baseline LOC, with 6--7
    identifiable concerns.
\end{itemize}

\subsection*{Chatty Component -- 3 occurrences}

A Chatty Component issues many fine-grained calls to a remote resource
(database, REST API, WebSocket broadcast) instead of batching. The baseline
is 1--2 I/O operations per user action.

\begin{itemize}
  \item \textbf{High -- \texttt{frontend/src/context/TodoContext.jsx}}:
    \texttt{reorderTasks()} and the undo/redo functions issue one
    \texttt{PATCH}/\texttt{PUT} request \emph{per task} via
    \texttt{Promise.all}, so an $n$-item list produces $n$ round-trips per
    action. This is unbounded and degrades linearly with list size -- easily
    10$\times$ the baseline for a modest list.

  \item \textbf{Medium -- \texttt{backend/src/routes/oidc.js}}: the
    \texttt{/oauth2/token} handler alone performs 5 SQLite reads and 2 writes
    (7 sequential DB calls) per single token exchange. Aggregated across all
    endpoints, the file makes 13+ fine-grained DB calls per authentication
    flow, approximately 6$\times$ the 2-call baseline.

  \item \textbf{Low -- \texttt{backend/src/ws/chat.js}}: on every incoming
    message the handler iterates over all connected clients and calls
    \texttt{JSON.stringify} independently for each one, instead of serializing
    once and broadcasting the buffer. At current scale this is minor but the
    pattern does not scale.
\end{itemize}

\subsection*{Hotspot -- 3 occurrences}

A Hotspot is a file with high change frequency in the git history. Baseline
is 1--2 commits. Low $\approx$ 3--4 commits; Medium $\approx$ 5--7 commits;
High $\geq$ 8 commits. Churn was measured over the full git history of the
repository (24 commits total at the time of analysis).

\begin{itemize}
  \item \textbf{High -- \texttt{backend/src/server.js}}: 14 commits (58\% of
    all commits). Every new metric type (GPU, processes, network, disk) was
    added here, making it the file most likely to receive future changes.

  \item \textbf{Medium -- \texttt{frontend/src/pages/MetricsPage.jsx}}: 5
    commits (21\% of all commits). Each backend metric addition was mirrored
    by a UI change in this file, confirming co-evolution with
    \texttt{server.js}.

  \item \textbf{Low -- \texttt{frontend/src/index.css}}: 4 commits. Styling
    adjustments accompany nearly every feature addition, keeping this file at
    a mildly elevated churn rate.
\end{itemize}

\subsection*{Architectural Hotspot -- 2 occurrences}

An Architectural Hotspot is a file that is simultaneously a Hotspot (high
churn) and a Hub-Like or God Component (high coupling or high complexity).
It represents the riskiest intersection of structural debt and active
development.

\begin{itemize}
  \item \textbf{High -- \texttt{backend/src/server.js}}: 14 commits (hotspot)
    $\times$ fan-out of 9 (hub) $\times$ 396 LOC (god component). All three
    indicators are at their maximum in the project. Every feature iteration
    touches the file that is already the most interconnected and the largest.
    Risk of regression with each change is extremely high.

  \item \textbf{Medium -- \texttt{frontend/src/pages/MetricsPage.jsx}}: 5
    commits (hotspot) combined with 353 LOC and 7 embedded sub-components
    (god component). Although its external coupling is low (only
    \texttt{useWebSocket} is imported), internal coupling is high and every
    backend metrics extension forces a change to this file.
\end{itemize}
