\textbf{Method.} The assessment used only evidence visible in the repository: static dependencies from ES module imports/exports, current file size (LOC), and change concentration from \texttt{commits.txt}. Across backend and frontend source files there are 24 implementation files; in the commit log, 18 of them appear exactly once, so a single touch was treated as the baseline for hotspot analysis.

\textbf{Intensity thresholds.} For this system, \emph{Low} means a minimal but observable occurrence above the baseline; \emph{Medium} means a clearly amplified occurrence, typically around 2--5$\times$ the baseline or a structurally relevant dependency problem; \emph{High} means a very concentrated occurrence, typically $>$5$\times$ the baseline or a file that combines several responsibilities and central dependencies.

\textbf{Cyclic Dependency (1 medium, 2 files).} One explicit cycle is present between \texttt{backend/src/server.js} and \texttt{backend/src/routes/metrics.js}: \texttt{server.js} imports \texttt{metrics.js} to mount the router, while \texttt{metrics.js} imports \texttt{getMetrics} from \texttt{server.js}. Only one pair is affected, so the smell is present but not widespread; therefore it was classified as \emph{Medium}.

\textbf{Hub-Like Dependency (not present).} No file showed both high fan-in and high fan-out at the same time. \texttt{backend/src/server.js} has high outgoing dependencies (14 imports), but only one incoming dependency from \texttt{routes/metrics.js}. \texttt{frontend/src/App.jsx} also has high outgoing dependencies (10 imports) but only one incoming dependency from \texttt{main.jsx}. Because the codebase lacks a component that is simultaneously a major consumer and supplier of dependencies, this smell was marked absent.

\textbf{God Component (1 high, 1 low, 2 files).} \texttt{backend/src/server.js} was rated \emph{High}: it has 344 LOC, 14 imports, and mixes HTTP bootstrapping, WebSocket setup, metrics collection, caching, hardware discovery, GPU/network/process sampling, and subscription broadcasting. \texttt{frontend/src/context/TodoContext.jsx} was rated \emph{Low}: at 115 LOC it is much smaller, but it still combines state management, HTTP access, undo/redo history, drag-and-drop persistence, action logging, and keyboard shortcuts. No other file showed the same degree of responsibility concentration with equally clear evidence.

\textbf{Chatty Component (1 high, 1 file).} \texttt{frontend/src/context/TodoContext.jsx} was rated \emph{High}. Its \texttt{reorderTasks} operation issues one \texttt{PATCH} request per task, and \texttt{undo}/\texttt{redo} iterate with one \texttt{PUT} per task. This creates request amplification proportional to list size, which is strong evidence of excessive inter-component communication. The rest of the system uses ordinary request/response or expected WebSocket traffic, so no additional chatty components were counted.

\textbf{Hotspot (1 high, 1 medium, 2 files).} Using one commit touch as baseline, \texttt{backend/src/server.js} is a \emph{High} hotspot with 11 touches, far above every other source file. \texttt{frontend/src/pages/MetricsPage.jsx} is a \emph{Medium} hotspot with 4 touches, which is materially above baseline but still much lower than \texttt{server.js}. Files touched only once were not counted as hotspots, and files touched twice were considered too weak to classify conservatively in this repository.

\textbf{Architectural Hotspot (1 high, 1 file).} \texttt{backend/src/server.js} is the only file that combines both dimensions required for this smell: high architectural centrality and high churn. It is the entry point of the backend, imports 14 modules, participates in the only dependency cycle, concentrates multiple responsibilities, and is also the most frequently modified file (11 touches). That combination justifies a single \emph{High} architectural hotspot.
